Stateless Model Checking with Data-Race Preemption Points

### 2015-11-18 pldi-16/evaluation.tex
minor touchup

\begin{table*}[t]
	\begin{center}
		\small
	\begin{tabular}{r|c||c|c|c|c|c||c|c||c|c}
		& {\bf Num.} & {\bf SSS-MC} & {\bf QS} & {\bf DR-only} & {\bf Nondet.} & {\bf Malloc-} &
		{\bf Mutual} & {\bf Avg. tested} & {\bf Total} & {\bf Untested} \\
		{\bf Test name} & {\bf tested} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf DR bugs} & {\bf recycle DRs} &
		{\bf time-outs} & {\bf subset SSes} & {\bf DR PPs} & {\bf DR PPs} \\
		\hline
		% FIXME: update FRMs
				% #test  sssmc   qs      dronly  nondets  FRMs   timeout comp.SSes DRPPs untested DRPPs
		{\tt bcast}	& 79	& 7	& 11	& 4	& 4	& 51	& 0	& -	& 912	& 107	\\
		{\tt join} 	& 79	& 14 	& 25	& 10	& 6	& 333	& 5	& 60.8	& 781	& 292	\\
		{\tt mx} 	& 79	& 1	& 10	& 9	& 1	& 7	& 0	& -	& 829	& 1	\\
		{\tt sem} 	& 79	& 10	& 17	& 6	& 5	& 140	& 29	& 73.3	& 753	& 279	\\
		{\tt signal} 	& 79	& 4	& 12	& 7	& 6	& 180	& 10	& 54.2	& 1118	& 391	\\
		{\tt rwlock} 	& 79	& 26	& 30	& 2	& 2	& 125	& 19	& 29.6	& 915	& 634	\\
		\hline
		{\tt sched} 	& 59	& 1	& 7	& 6	& 4	& 0	& 0	& -	& 144	& 3	\\
		{\tt alarm} 	& 44	& 5	& 21	& 17	& 3	& 35 	& 22	& 9.1	& 115	& 89	\\
		{\tt wait} 	& 52	& 23	& 30	& 7	& 1	& 31	& 8	& 28.0	& 142	& 31	\\
		\hline
		{\bf Total}	& 629	& 91	& 163	& 68	& 32	& 902	& 93	& 42.6 	& 5709	& 1827	\\
	\end{tabular}
	\end{center}
	\caption{Summary of bugs and data races found by each test program.
		SSS-MC is the control; QS is \quicksand.
		``DR-only bugs'' counts among \quicksand's bugs how many required data-race PPs to expose (\sect{\ref{sec:eval-sssmc}});
	among those, ``Nondeterministic DR bugs'' counts how many candidates required MC integration to identify (\sect{\ref{sec:eval-falseneg}}).
	``Malloc-recycle DRs'' counts how many false positives we suppressed (\sect{\ref{sec:eval-falsepos}}).
	``Mutual time-outs'' counts how often both SSS-MC and \quicksand~timed out with no bug found;
	among those, ``Average tested subset SSes'' counts how many partial verifications \quicksand~provided on average for each test (\sect{\ref{sec:eval-sssmc}}).
	``Total DR PPs'' counts how many unique data-racing instructions we identified among tests with no bugs found;
	among those, ``Untested DR PPs'' counts how many could not be checked in the time limit (\sect{\ref{sec:future}}).
		}
	\label{tab:drbugs}
\end{table*}

>>>>

\begin{table*}[t]
	\begin{center}
		\small
	\begin{tabular}{r|c||c|c|c|c|c||c|c||c|c}
		& {\bf Num.} & {\bf SSS-MC} & {\bf QS} & {\bf DR-only} & {\bf Nondet.} & {\bf Malloc-} &
		{\bf Mutual} & {\bf Avg. tested} & {\bf Total} & {\bf Untested} \\
		{\bf Test name} & {\bf tested} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf DR bugs} & {\bf recycle DRs} &
		{\bf time-outs} & {\bf subset SSes} & {\bf DR PPs} & {\bf DR PPs} \\
		\hline
		% FIXME: update FRMs
				% #test  sssmc   qs      dronly  nondets  FRMs   timeout comp.SSes DRPPs untested DRPPs
		{\tt bcast}	& 79	& 7	& 11	& 4	& 4	& 51	& 0	& -	& 912	& 107	\\
		{\tt join} 	& 79	& 14 	& 25	& 10	& 6	& 333	& 5	& 60.8	& 781	& 292	\\
		{\tt mx} 	& 79	& 1	& 10	& 9	& 1	& 7	& 0	& -	& 829	& 1	\\
		{\tt sem} 	& 79	& 10	& 17	& 6	& 5	& 140	& 29	& 73.3	& 753	& 279	\\
		{\tt signal} 	& 79	& 4	& 12	& 7	& 6	& 180	& 10	& 54.2	& 1118	& 391	\\
		{\tt rwlock} 	& 79	& 26	& 30	& 2	& 2	& 125	& 19	& 29.6	& 915	& 634	\\
		\hline
		{\tt sched} 	& 59	& 1	& 7	& 6	& 4	& 0	& 0	& -	& 144	& 3	\\
		{\tt alarm} 	& 44	& 5	& 21	& 17	& 3	& 35 	& 22	& 9.1	& 115	& 89	\\
		{\tt wait} 	& 52	& 23	& 30	& 7	& 1	& 31	& 8	& 28.0	& 142	& 31	\\
		\hline
		{\bf Total}	& 629	& 91	& 163	& 68	& 32	& 902	& 93	& 42.6 	& 5709	& 1827	\\
	\end{tabular}
	\end{center}
	\caption{Summary of bugs and data races found by each test program.
		SSS-MC is the control; QS is \quicksand.
		``DR-only bugs'' counts among \quicksand's bugs how many required data-race PPs to expose (\sect{\ref{sec:eval-sssmc}});
	among those, ``Nondeterministic DR bugs'' counts how many candidates required MC integration to identify (\sect{\ref{sec:eval-falseneg}}).
	``Malloc-recycle DRs'' counts how many false positives we suppressed (\sect{\ref{sec:eval-falsepos}}).
	``Mutual time-outs'' counts how often both SSS-MC and \quicksand~timed out with no bug found;
	among those, ``Average tested subset SSes'' counts how many partial verifications \quicksand~provided on average for each test (\sect{\ref{sec:eval-sssmc}}).
	``Total DR PPs'' counts how many unique data-racing instructions we identified among tests where we found no bugs;
	among those, ``Untested DR PPs'' counts how many could not be checked in the time limit (\sect{\ref{sec:future}}).
		}
	\label{tab:drbugs}
\end{table*}
